Data Cleaning logbook

### 2018-12-06 scripts/data_cleaning_logbook.Rmd
Added missing zero's for fish and inverts. This fixes #48

```{r}
invert <- read.csv(here::here("raw_data", "invert_data.csv"), strip.white = T, stringsAsFactors = F) %>% 
  janitor::clean_names() %>% 
  rename(generoespecie = genero_especie) %>% 
  filter(comunidad %in% c("Isla Natividad", "Maria Elena", "Punta Herrero")) %>% 
  filter(!is.na(rc),
         rc %in% c("La Plana / Las Cuevas - La Dulce / Babencho",
                   "Cabezo - Cabezo (Control)",
                   "Manchon - Manchon (Control)",
                   "El Faro - El Faro (Control)")) %>% 
  filter(!(rc %in% c("El Faro - El Faro (Control)") & ano == 2012)) %>% 
  filter(between(abundancia, 0.1, 100)) %>% 
  group_by(comunidad, ano, rc, sitio, zona, transecto, generoespecie) %>% 
  summarize(abundancia = sum(abundancia)) %>% 
  ungroup() %>% 
  mutate(year = case_when(comunidad == "Isla Natividad" ~ ano - 2006,
                         comunidad == "Maria Elena" ~ ano - 2012,
                         TRUE ~ ano - 2013)) %>% 
  select(comunidad, ano, year, rc, sitio, zona, transecto, generoespecie, abundancia) %>% 
  arrange()
```

@@

```{r}
fish <- read.csv(here::here("raw_data", "fish_data.csv"), strip.white = T, stringsAsFactors = F) %>% 
  janitor::clean_names() %>% 
  rename(generoespecie = genero_especie) %>% 
  filter(comunidad %in% c("Isla Natividad", "Maria Elena", "Punta Herrero")) %>% 
  filter(!is.na(rc),
         rc %in% c("La Plana / Las Cuevas - La Dulce / Babencho",
                   "Cabezo - Cabezo (Control)",
                   "Manchon - Manchon (Control)",
                   "El Faro - El Faro (Control)")) %>% 
  filter(!(rc %in% c("El Faro - El Faro (Control)") & ano == 2012)) %>% 
  filter(abundancia > 0) %>% 
  mutate(generoespecie = case_when(generoespecie == "Cephalopholis cruentatus" ~ "Cephalopholis cruentata",
                                   generoespecie == "Haemulon macrostomun" ~ "Haemulon macrostomum",
                                   generoespecie == "Xcochin spp" ~ "Balistes capriscus",
                                   generoespecie == "Pterois volitans/miles" ~ "Pterois volitans",
                                   generoespecie == "Mycteroperca spp" ~ "Mycteroperca",
                                   generoespecie == "Chromis spp" ~ "Chromis",
                                   generoespecie == "Damisela spp" ~ "Stegastes",
                                   generoespecie == "Haemulon spp" ~ "Haemulon",
                                   generoespecie == "Lancero spp" ~ "Acanthurus",
                                   generoespecie == "Kyphosus sectatrix/incisor" ~ "Kyphosus",
                                   generoespecie == "Sebastes spp" ~ "Sebastes",
                                   generoespecie == "Loro spp" ~ "Scarus",
                                   generoespecie == "Lutjanus spp" ~ "Lutjanus",
                                   generoespecie == "Mariposa spp" ~ "Chaetodon",
                                   generoespecie == "Pluma spp" ~ "Calamus pennatula",
                                   generoespecie == "Sparisoma aurolineatum" ~ "Sparisoma aurofrenatum",
                                   generoespecie == "Vieja spp" ~ "Bodianus rufus",
                                   TRUE ~ generoespecie)) %>% 
  left_join(species_bio, by = c("generoespecie")) %>% 
  group_by(comunidad, ano, rc, sitio, zona, transecto, generoespecie, talla, a,b) %>% 
  summarize(abundancia = sum(abundancia)) %>% 
  ungroup() %>% 
  mutate(year = case_when(comunidad == "Isla Natividad" ~ ano - 2006,
                         comunidad == "Maria Elena" ~ ano - 2012,
                         TRUE ~ ano - 2013)) %>% 
  select(comunidad, ano, year, rc, sitio, zona, transecto, generoespecie, talla, abundancia, a, b) %>% 
  arrange() %>% 
  drop_na(a, b)
```

>>>>

```{r}
invert <- read.csv(here::here("raw_data", "invert_data.csv"), strip.white = T, stringsAsFactors = F) %>% 
  janitor::clean_names() %>% 
  rename(generoespecie = genero_especie) %>% 
  filter(comunidad %in% c("Isla Natividad", "Maria Elena", "Punta Herrero")) %>% 
  filter(!is.na(rc),
         rc %in% c("La Plana / Las Cuevas - La Dulce / Babencho",
                   "Cabezo - Cabezo (Control)",
                   "Manchon - Manchon (Control)",
                   "El Faro - El Faro (Control)")) %>% 
  filter(!(rc %in% c("El Faro - El Faro (Control)") & ano == 2012)) %>% 
  filter(between(abundancia, 0.1, 100)) %>% 
  group_by(comunidad, ano, rc, sitio, zona, transecto, generoespecie) %>% 
  summarize(abundancia = sum(abundancia)) %>% 
  ungroup() %>% 
  mutate(year = case_when(comunidad == "Isla Natividad" ~ ano - 2006,
                         comunidad == "Maria Elena" ~ ano - 2012,
                         TRUE ~ ano - 2013)) %>% 
  spread(generoespecie, abundancia, fill = 0) %>% 
  gather(generoespecie, abundancia, -c("comunidad", "ano", "year", "rc", "sitio", "zona", "transecto")) %>% 
  select(comunidad, ano, year, rc, sitio, zona, transecto, generoespecie, abundancia) %>% 
  arrange()
```

@@

```{r}
fish <- read.csv(here::here("raw_data", "fish_data.csv"), strip.white = T, stringsAsFactors = F) %>% 
  janitor::clean_names() %>% 
  rename(generoespecie = genero_especie) %>% 
  filter(comunidad %in% c("Isla Natividad", "Maria Elena", "Punta Herrero")) %>% 
  filter(!is.na(rc),
         rc %in% c("La Plana / Las Cuevas - La Dulce / Babencho",
                   "Cabezo - Cabezo (Control)",
                   "Manchon - Manchon (Control)",
                   "El Faro - El Faro (Control)")) %>% 
  filter(!(rc %in% c("El Faro - El Faro (Control)") & ano == 2012)) %>% 
  filter(abundancia > 0) %>% 
  mutate(generoespecie = case_when(generoespecie == "Cephalopholis cruentatus" ~ "Cephalopholis cruentata",
                                   generoespecie == "Haemulon macrostomun" ~ "Haemulon macrostomum",
                                   generoespecie == "Xcochin spp" ~ "Balistes capriscus",
                                   generoespecie == "Pterois volitans/miles" ~ "Pterois volitans",
                                   generoespecie == "Mycteroperca spp" ~ "Mycteroperca",
                                   generoespecie == "Chromis spp" ~ "Chromis",
                                   generoespecie == "Damisela spp" ~ "Stegastes",
                                   generoespecie == "Haemulon spp" ~ "Haemulon",
                                   generoespecie == "Lancero spp" ~ "Acanthurus",
                                   generoespecie == "Kyphosus sectatrix/incisor" ~ "Kyphosus",
                                   generoespecie == "Sebastes spp" ~ "Sebastes",
                                   generoespecie == "Loro spp" ~ "Scarus",
                                   generoespecie == "Lutjanus spp" ~ "Lutjanus",
                                   generoespecie == "Mariposa spp" ~ "Chaetodon",
                                   generoespecie == "Pluma spp" ~ "Calamus pennatula",
                                   generoespecie == "Sparisoma aurolineatum" ~ "Sparisoma aurofrenatum",
                                   generoespecie == "Vieja spp" ~ "Bodianus rufus",
                                   TRUE ~ generoespecie)) %>% 
  left_join(species_bio, by = c("generoespecie")) %>% 
  group_by(comunidad, ano, rc, sitio, zona, transecto, generoespecie, talla, a,b) %>% 
  summarize(abundancia = sum(abundancia)) %>% 
  ungroup() %>% 
  mutate(year = case_when(comunidad == "Isla Natividad" ~ ano - 2006,
                         comunidad == "Maria Elena" ~ ano - 2012,
                         TRUE ~ ano - 2013)) %>% 
  spread(generoespecie, abundancia, fill = 0) %>% 
  gather(generoespecie, abundancia, -c("comunidad", "ano", "year", "rc", "sitio", "zona", "transecto", "talla", "a", "b")) %>% 
  select(comunidad, ano, year, rc, sitio, zona, transecto, generoespecie, talla, abundancia, a, b) %>% 
  arrange() %>% 
  drop_na(a, b)
```
